% ===========================================================================
% Section 6: Ablation Studies
% ===========================================================================

We conduct two ablation studies to analyze the contribution of individual components within \ours{}: the evaluation tool configuration (RQ3, \S\ref{subsec:rq3}) and the structure-aware retrieval tools (RQ4, \S\ref{subsec:rq4}).
Table~\ref{tab:full_ablation} additionally provides a consolidated view of all ablation variants on a single metric (F1) for cross-component comparison.

\noindent\textit{Note on baseline values.}
Tables~\ref{tab:rq3} and~\ref{tab:rq4} report results from their respective experiment runs; the ``Full system'' baseline is shared across both.
Table~\ref{tab:full_ablation} consolidates values from these individual RQ tables for cross-component comparison.
Minor differences between the Full system F1 here and Table~\ref{tab:rq1_main} (typically $\leq 0.02$) arise from non-determinism in LLM API calls at temperature~$= 0$.

% ---------------------------------------------------------------------------
\subsection{RQ3: Evaluation Tool Variants}
\label{subsec:rq3}
% ---------------------------------------------------------------------------

\textbf{Does 4-dimensional quality assessment as an agent tool improve decision-making compared to 1-dimensional or no evaluation?}

We compare three variants of the evaluation tool within the \ours{} pipeline:
\begin{itemize}
    \item \textbf{Agent + 4D}: Full 4-dimensional evaluation (Relevance, Coverage, Specificity, Sufficiency), with per-dimension scores and refinement feedback.
    \item \textbf{Agent + 1D}: Single holistic quality score (0--100) with refinement feedback but no dimensional breakdown.
    \item \textbf{Agent w/o Eval}: Evaluation tool removed entirely; the agent relies solely on its own reasoning about passage quality.
\end{itemize}

\begin{table*}[t]
\centering
\caption{Evaluation tool ablation (RQ3, $n = 200$). The w/o Eval variant consistently underperforms variants with evaluation, confirming the evaluation tool's role as a quality gate. 1D and 4D perform comparably, with 1D marginally ahead on 3/4 datasets. Best per dataset in \textbf{bold}.}
\label{tab:rq3}
\resizebox{\textwidth}{!}{%
\begin{tabular}{l cc cc cc cc}
\toprule
& \multicolumn{2}{c}{\textbf{HotpotQA}} & \multicolumn{2}{c}{\textbf{2WikiMultiHopQA}} & \multicolumn{2}{c}{\textbf{MuSiQue}} & \multicolumn{2}{c}{\textbf{FinanceBench}} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
\textbf{Variant} & EM & F1 & EM & F1 & EM & F1 & EM & F1 \\
\midrule
Agent + 4D     & .525 & .674 & \textbf{.500} & \textbf{.611} & \textbf{.345} & .449 & .180 & .411 \\
Agent + 1D     & \textbf{.530} & \textbf{.680} & .505 & .608 & .340 & \textbf{.455} & \textbf{.187} & \textbf{.421} \\
Agent w/o Eval & .525 & .674 & .475 & .580 & .340 & .438 & .153 & .387 \\
\midrule
\multicolumn{1}{r}{\textit{$\Delta$ 1D vs.\ w/o}} & $+.005$ & $+.006$ & $+.030$ & $+.028$ & $=$ & $+.017$ & $+.034$ & $+.034$ \\
\multicolumn{1}{r}{\textit{$\Delta$ 4D vs.\ w/o}} & $=$ & $=$ & $+.025$ & $+.031$ & $+.005$ & $+.011$ & $+.027$ & $+.024$ \\
\bottomrule
\end{tabular}
}% end resizebox
\end{table*}

\paragraph{Evaluation as quality gate}
At the $n = 200$ scale, a clear pattern emerges that was not discernible in pilot experiments: the \textbf{w/o Eval variant consistently ranks last} across all four datasets (F1: 0.674, 0.580, 0.438, 0.387).
The quality gap is most pronounced on datasets where retrieval is challenging: 2WikiMultiHopQA ($\Delta = +0.028$--$0.031$ for 1D/4D over w/o Eval) and FinanceBench ($\Delta = +0.024$--$0.034$).
On HotpotQA, where retrieval is relatively easy, the evaluation tool provides negligible benefit ($\Delta \leq 0.006$).

This confirms that the evaluation tool functions as a \emph{quality gate mechanism}: by providing an explicit quality checkpoint, it prevents the agent from terminating prematurely with insufficient evidence.
Without the gate, the agent must rely entirely on its own implicit quality assessment, which proves less reliable on difficult retrieval tasks.

\paragraph{1D vs.\ 4D: granularity is secondary}
The 1D holistic score marginally outperforms the 4D dimensional breakdown on 3/4 datasets (F1 differences $\leq 0.010$).
This suggests that the \emph{presence} of evaluation matters more than its \emph{granularity}---a single quality score with feedback is sufficient for the agent to make informed refinement decisions.
The 4D variant retains value as a diagnostic tool, providing interpretable dimension-level feedback (\eg, ``Coverage is low---consider searching for the second entity'') that can aid debugging and analysis, even when it does not improve aggregate scores.

% ---------------------------------------------------------------------------
\subsection{RQ4: Structure-Aware Retrieval Tools}
\label{subsec:rq4}
% ---------------------------------------------------------------------------

\textbf{Do structure-aware retrieval tools (section index, terminology mapping) improve agent performance?}

We evaluate four configurations across all datasets to assess whether document structure navigation tools provide benefits beyond standard keyword search:
\begin{itemize}
    \item \textbf{Full Tools}: All tools including \texttt{list\_document\_sections} and \texttt{get\_terminology}.
    \item \textbf{w/o Section}: Section browsing tool removed.
    \item \textbf{w/o Term}: Terminology mapping tool removed.
    \item \textbf{w/o Both}: Both structure-aware tools removed (core tools only).
\end{itemize}

\begin{table*}[t]
\centering
\caption{Structure-aware tool ablation (RQ4, $n = 200$). Structure tools provide benefits on complex, multi-hop datasets (MuSiQue, FinanceBench) but not on simpler Wikipedia-based datasets (HotpotQA, 2WikiMultiHopQA). Best per dataset in \textbf{bold}.}
\label{tab:rq4}
\resizebox{\textwidth}{!}{%
\begin{tabular}{l cc cc cc cc}
\toprule
& \multicolumn{2}{c}{\textbf{HotpotQA}} & \multicolumn{2}{c}{\textbf{2WikiMultiHopQA}} & \multicolumn{2}{c}{\textbf{MuSiQue}} & \multicolumn{2}{c}{\textbf{FinanceBench}} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
\textbf{Variant} & EM & F1 & EM & F1 & EM & F1 & EM & F1 \\
\midrule
Full Tools     & \textbf{.525} & .674 & .500 & .611 & \textbf{.345} & \textbf{.449} & \textbf{.180} & \textbf{.411} \\
w/o Section    & .495 & .656 & \textbf{.505} & \textbf{.621} & .335 & .445 & .153 & .390 \\
w/o Term       & .500 & .654 & .480 & .593 & .335 & .433 & .153 & .388 \\
w/o Both       & \textbf{.525} & \textbf{.677} & .485 & .597 & .320 & .422 & .153 & .384 \\
\midrule
\multicolumn{1}{r}{\textit{$\Delta$ Full vs.\ w/o Both}} & $=$ & $-.003$ & $+.015$ & $+.014$ & $+.025$ & $+.027$ & $+.027$ & $+.027$ \\
\bottomrule
\end{tabular}
}% end resizebox
\end{table*}

\paragraph{Dataset-dependent benefit}
Table~\ref{tab:rq4} reveals that the value of structure-aware tools is \emph{dataset-dependent}:

\begin{itemize}
    \item \textbf{MuSiQue and FinanceBench}: Full Tools achieves the highest F1 on both datasets, with consistent $+0.027$ F1 improvement over w/o Both.
    On MuSiQue, this reflects the benefit of hierarchical document navigation for 3--4 hop questions that require traversing multiple document sections.
    On FinanceBench, section browsing helps navigate the structured hierarchy of SEC filings (10-K sections, financial statement tables).

    \item \textbf{HotpotQA}: Removing both tools marginally \emph{improves} F1 (0.677 vs.\ 0.674, $\Delta = +0.003$).
    Wikipedia articles used in HotpotQA have simple, flat structures where section navigation provides no advantage over keyword-based search.

    \item \textbf{2WikiMultiHopQA}: The w/o Section variant achieves the highest F1 (0.621 vs.\ 0.611 for Full), a mixed result.
    We attribute this to the action space effect: additional tools increase the agent's decision complexity, and on datasets where these tools provide marginal retrieval value, the expanded action space can slightly degrade performance.
\end{itemize}

\paragraph{Terminology tool}
The \texttt{get\_terminology} tool shows minimal impact across all datasets: removing it (w/o Term vs.\ Full) yields small, inconsistent changes ($|\Delta| \leq 0.020$).
This is consistent with the tool frequency analysis (Table~\ref{tab:tool_usage}), where \texttt{get\_terminology} is called $< 0.1$ times per question.
The vocabulary gap between user questions and corpus language is not a primary bottleneck for these benchmarks, though the tool may prove more valuable in highly specialized domains with extensive jargon (\eg, legal, medical).

\paragraph{Extensibility framework}
While the aggregate benefit of structure tools is modest, the \emph{architecture} that enables domain-specific tool integration is a meaningful contribution.
The agent's ability to selectively invoke structure tools on datasets where they help (MuSiQue, FinanceBench) and ignore them where they do not (HotpotQA) demonstrates the viability of an extensible tool framework.
Adding new domain-specific tools (\eg, table parsers for financial data, citation resolvers for scientific documents) requires only implementing the tool function and registering it with the agent---no pipeline modification is needed.

% ---------------------------------------------------------------------------
\subsection{Consolidated Ablation Summary}
\label{subsec:ablation_summary}
% ---------------------------------------------------------------------------

Table~\ref{tab:full_ablation} provides a consolidated view of all ablation variants on F1.

\begin{table*}[t]
\centering
\caption{Consolidated ablation results (F1, Gemini Flash Lite, $n = 200$). Each variant modifies one component of the full \ours{} pipeline. Best per dataset in \textbf{bold}.}
\label{tab:full_ablation}
\resizebox{\textwidth}{!}{%
\begin{tabular}{ll cccc}
\toprule
\textbf{Component} & \textbf{Variant} & \textbf{HotpotQA} & \textbf{2Wiki} & \textbf{MuSiQue} & \textbf{FinanceBench} \\
\midrule
Full system & Agent + All Tools          & .674 & .611 & .449 & .411 \\
\midrule
\multirow{2}{*}{Evaluation (RQ3)}
  & 1D Evaluation              & \textbf{.680} & .608 & \textbf{.455} & \textbf{.421} \\
  & w/o Evaluate Tool          & .674 & .580 & .438 & .387 \\
\midrule
Retrieval (RQ2)
  & w/o Search (no re-retrieval) & .621 & .541 & .420 & .393 \\
\midrule
\multirow{2}{*}{Structure (RQ4)}
  & w/o Section Index          & .656 & \textbf{.621} & .445 & .390 \\
  & w/o Term Index             & .654 & .593 & .433 & .388 \\
\midrule
Agent (RQ1)
  & w/o Agent (for-loop)       & .636 & .495 & .399 & .400 \\
\midrule
Prompt (RQ5)
  & Manual Prompt              & .608 & .496 & .481 & .256 \\
\bottomrule
\end{tabular}
}% end resizebox
\end{table*}

\paragraph{Component importance ranking}
Three observations emerge from the consolidated view:
\begin{enumerate}
    \item \textbf{Re-retrieval is the most critical tool}: removing search (the agent's ability to re-retrieve) causes the largest consistent drop (F1 $-0.018$ to $-0.070$ vs.\ Full), confirming that iterative search is the agent's primary mechanism for quality improvement.

    \item \textbf{Agentic reasoning outperforms fixed loops}: the for-loop variant consistently underperforms the full agent on multi-hop datasets (2Wiki: $-0.116$, MuSiQue: $-0.050$), demonstrating the value of autonomous tool selection over predetermined iteration.
    FinanceBench is the sole exception (Loop 0.400 vs.\ Agent 0.411), consistent with the retrieval space saturation effect.

    \item \textbf{MuSiQue Manual prompt anomaly}: the Manual prompt achieves 0.481 on MuSiQue, exceeding the Full system (0.449).
    We attribute this to the Manual variant's simpler pipeline (no agent overhead) combined with manually tuned prompts that happen to suit MuSiQue's specific question patterns.
    However, Manual collapses on FinanceBench (0.256, lowest overall), highlighting its fragility across domains.
\end{enumerate}
