% ===========================================================================
% Section 8: Conclusion
% ===========================================================================

We presented \ours{}, a framework that replaces fixed-loop self-corrective RAG with a ReAct-based agent equipped with six specialized tools for autonomous retrieval refinement.
Implemented as a DSPy declarative pipeline, the framework enables both structured prompting through typed Signatures and automatic optimization through BootstrapFewShot and MIPROv2.

Our experiments across four datasets ($n = 200$) with bootstrap significance testing and cross-model validation demonstrated three principal findings.
First, agentic refinement provides \emph{complexity-dependent} improvements: statistically significant gains on complex multi-hop questions (F1 $+0.089$ on 2WikiMultiHopQA, $p < 0.001$) with diminishing benefits on simpler tasks and a boundary condition on small corpora (FinanceBench).
Second, DSPy's typed Signatures improve F1 by 0.071--0.164 over manual prompt engineering on three of four datasets, with BootstrapFewShot achieving the best F1 on all four datasets and recovering performance even where Signatures alone underperform manual prompts.
Third, cross-model validation reveals a \emph{model--pipeline interaction effect}: reasoning-oriented models (gpt-5-mini) exhibit higher refusal rates in agentic pipelines, suggesting that pipeline selection should account for the base model's reasoning characteristics.

Trajectory analysis reveals emergent structured protocols (decompose--search--evaluate) that arise from the combination of typed Signatures and ReAct reasoning, without hard-coded orchestration.
Ablation studies confirm that the evaluation tool serves as a quality gate mechanism, with 1D holistic scores proving sufficient. Structure-aware tools provide dataset-dependent benefits on complex documents, and re-retrieval emerges as the agent's most critical capability.

\paragraph{Future Work}
Several directions merit investigation:
(1)~evaluating structure-aware tools on documents with rich hierarchical structure (\eg, legal contracts, technical manuals);
(2)~reducing agent latency through parallel tool execution, speculative decoding, or agent module distillation;
(3)~addressing the Reasoning Model Refusal Asymmetry through calibrated refusal thresholds or forced-answer fallback mechanisms;
and (4)~extending the framework with additional domain-specific tools for tasks such as table parsing, cross-document reasoning, and temporal analysis.
