% ===========================================================================
% Section 7: Discussion
% ===========================================================================

% ---------------------------------------------------------------------------
\subsection{Complexity-Dependent Improvement}
\label{subsec:complexity}
% ---------------------------------------------------------------------------

The most consistent finding across our experiments is that the agentic advantage is \emph{proportional to question complexity}.
On simple 2-hop questions (HotpotQA), \ours{} performs comparably to single-pass baselines ($\Delta \leq +0.022$ F1, not significant).
On complex 2--4 hop questions (2WikiMultiHopQA), the improvement is substantial ($+0.089$ F1, $p < 0.001$) and consistent across all metrics.
MuSiQue shows a positive but non-significant trend ($+0.039$ F1), positioning it between the simple and complex extremes.

This gradient has a natural explanation: complex multi-hop questions benefit from the agent's ability to \emph{adaptively compose retrieval strategies}---decomposing questions, searching sub-questions independently, and evaluating the combined evidence.
Simple questions that can be answered from a single well-retrieved passage set do not require this adaptive strategy, and the additional reasoning overhead provides no measurable benefit.

This suggests a practical deployment guideline: \ours{} should be selectively applied to questions identified as complex or multi-hop, while simpler questions can be routed to faster single-pass pipelines.
This aligns with Adaptive-RAG's~\cite{jeong2024adaptiverag} approach of routing by question complexity, though our system handles the complex-question case more effectively through tool-augmented reasoning.

% ---------------------------------------------------------------------------
\subsection{Boundary Conditions: Retrieval Space Saturation}
\label{subsec:boundary}
% ---------------------------------------------------------------------------

Results on FinanceBench reveal a consistent boundary condition for agentic refinement: \ours{} underperforms Loop Refinement on both Gemini ($-0.014$ F1) and gpt-5-mini ($-0.011$ F1), with Naive RAG achieving the highest LLM-as-Judge scores on both models (0.580 and 0.540, respectively).
Statistical testing confirms that no pairwise comparison on FinanceBench reaches significance, indicating a genuine ceiling rather than sampling noise.

We identify three contributing factors:

\paragraph{Small retrieval space}
FinanceBench contains only 211 passages, compared to 5,000--66,000 for the multi-hop datasets.
In such a constrained retrieval space, the initial hybrid retrieval already surfaces most relevant passages.
The agent's iterative search provides diminishing returns because there are few additional passages to discover---a phenomenon we term \emph{retrieval space saturation}.
This is supported by the compressed performance range: the top four pipelines span only 0.019 F1 (0.381--0.400) on Gemini.

\paragraph{Answer distortion through over-refinement}
The LLM-as-Judge results reveal that Naive RAG produces the best-judged answers on FinanceBench.
This suggests that iterative refinement---whether agentic or loop-based---can \emph{distort} answers on domain-specific questions.
Financial questions often require precise numerical answers or specific terminology; additional refinement cycles may introduce hedging language, rounding errors, or over-elaboration that reduce answer precision.
We observe that agentic answers average 33.9 words per response compared to 12.7 for reference answers, indicating verbosity that penalizes exact match scoring.

\paragraph{Evaluation score miscalibration}
The evaluation tool produces higher scores on FinanceBench questions that ultimately receive lower F1 scores.
Questions with evaluation scores $\geq 80$ achieve average F1 of only 0.289, while questions where evaluation errors occur achieve higher F1 (0.452).
This suggests that the evaluation tool is not well-calibrated for domain-specific retrieval quality, potentially triggering unnecessary refinement cycles when the initial retrieval is already adequate.

These findings imply that agentic refinement is most valuable when the retrieval space is large enough to benefit from iterative exploration and when answer precision is compatible with multiple retrieval passes.
Enterprise deployments on small, well-curated corpora may benefit more from simpler pipeline configurations.

% ---------------------------------------------------------------------------
\subsection{Model--Pipeline Interaction Effect}
\label{subsec:model_interaction}
% ---------------------------------------------------------------------------

The cross-model experiment reveals a previously uncharacterized interaction between model architecture and pipeline design.
With Gemini Flash Lite (a generation-focused model), \ours{} consistently outperforms CRAG on multi-hop datasets.
With gpt-5-mini (a reasoning-focused model), the pattern \emph{reverses}: CRAG outperforms \ours{} on 2WikiMultiHopQA ($+0.086$ F1, $p = 0.004$).

\paragraph{Reasoning Model Refusal Asymmetry}
We trace this reversal to differential refusal behavior across pipeline architectures.
Table~\ref{tab:refusal} quantifies the answer refusal rates (responses containing ``Cannot determine,'' ``insufficient information,'' or equivalent).

\begin{table}[t]
\centering
\caption{Answer refusal rates (\%) on 2WikiMultiHopQA by model and pipeline. Reasoning models (gpt-5-mini) refuse more frequently in agentic pipelines, while generation models (Gemini) show the opposite pattern.}
\label{tab:refusal}
\begin{tabular}{lcccc}
\toprule
& \multicolumn{2}{c}{\textbf{gpt-5-mini}} & \multicolumn{2}{c}{\textbf{Gemini}} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5}
\textbf{Pipeline} & \textbf{\ours{}} & \textbf{CRAG} & \textbf{\ours{}} & \textbf{CRAG} \\
\midrule
Refusal rate    & 30\% & 18\% & 14\% & 34\% \\
F1 (all)        & .551 & .637 & .584 & .255 \\
F1 (non-refused) & .712 & -- & -- & -- \\
\bottomrule
\end{tabular}
\end{table}

The mechanism operates as follows:
\begin{itemize}
    \item \textbf{gpt-5-mini in ReAct}: The model's reasoning capabilities lead it to apply stringent evidentiary standards.
    Even when the evaluation tool reports adequate quality (mean score 66, above the threshold of 40), the agent independently judges the evidence insufficient and produces a refusal response.
    Each refusal scores F1 $= 0.0$, dragging the average down.
    When the agent \emph{does} answer, its F1 is 0.712---substantially higher than CRAG's overall 0.637---indicating that refusals, not answer quality, drive the performance gap.

    \item \textbf{CRAG's forced-answer pipeline}: CRAG's rigid judge--correct--generate architecture does not permit the model to refuse.
    The pipeline always produces an answer, converting some refusal-prone questions into correct (or partially correct) responses.

    \item \textbf{Gemini in ReAct}: As a generation-focused model, Gemini is less conservative in its evidentiary standards.
    It refuses only 14\% of the time in the agentic pipeline, allowing \ours{} to outperform CRAG (which, with Gemini, refuses 34\% due to CRAG's stricter binary evaluation triggering more ``incorrect'' classifications).
\end{itemize}

\paragraph{Implications}
This finding has two practical implications.
First, pipeline selection should consider the base model's reasoning characteristics: reasoning-oriented models may benefit from forced-answer pipelines or calibrated refusal thresholds, while generation-oriented models are better suited to agentic frameworks.
Second, the refusal asymmetry suggests that evaluation tools should be designed to provide calibrated confidence signals that interact predictably with different model types, rather than relying on the model's implicit evidentiary standards.

\paragraph{Efficiency perspective}
Despite CRAG's higher F1 with gpt-5-mini on 2WikiMultiHopQA, it requires 45.2 LLM calls per question (147.8 seconds) compared to 9.9 calls (45.7 seconds) for \ours{}---a 4.6$\times$ cost premium.
Combined with Gemini Flash Lite, \ours{} achieves the optimal cost--performance balance across our experimental configurations.

% ---------------------------------------------------------------------------
\subsection{Latency--Quality Trade-off}
\label{subsec:tradeoff}
% ---------------------------------------------------------------------------

\ours{} incurs 4--5$\times$ latency overhead compared to Loop Refinement (14--17s vs.\ 2--4s per question on Gemini).
This trade-off must be evaluated in context:

\begin{itemize}
    \item \textbf{Absolute latency.} 15 seconds per question is acceptable for many enterprise knowledge management scenarios where answer quality takes precedence over response time (\eg, compliance checking, due diligence, research assistance).

    \item \textbf{Cost attribution.} The latency is dominated by LLM API calls (5--6 tool invocations per question, each requiring LLM inference). With faster or locally deployed models, the absolute latency would decrease proportionally.

    \item \textbf{Quality payoff.} The F1 improvement of $+0.089$ on 2WikiMultiHopQA ($p < 0.001$) represents a statistically significant quality gain that justifies the latency cost in accuracy-critical applications.

    \item \textbf{Selective deployment.} As discussed in \S\ref{subsec:complexity}, the agentic approach should be selectively applied to complex questions.
    A two-tier system that routes simple questions to Single-Pass (3--5s) and complex questions to \ours{} (14--17s) would achieve an effective average latency well below 15s while capturing the quality benefits.
\end{itemize}

% ---------------------------------------------------------------------------
\subsection{DSPy: Structure vs.\ Optimization}
\label{subsec:dspy_discussion}
% ---------------------------------------------------------------------------

The RQ5 results reveal an important decomposition of DSPy's contribution:

The \emph{structural benefit}---replacing manual JSON prompts with typed Signatures---yields F1 improvements of $+0.071$--$0.164$ on three of four datasets without any optimization.
This benefit is essentially ``free'': it requires no training data, no optimization compute, and no hyperparameter tuning.
However, the structural benefit is not universal: on MuSiQue, Unopt substantially underperforms Manual ($-0.070$ F1), indicating that typed Signature constraints can conflict with question patterns that benefit from free-form generation.

The \emph{optimization benefit}---BootstrapFewShot and MIPROv2---compensates for this limitation.
BootstrapFewShot is the most consistently effective optimizer, achieving best F1 on all four datasets.
Critically, on MuSiQue where Unopt underperforms Manual, Bootstrap still achieves the overall best F1 ($+0.078$ over Manual), demonstrating that automatic optimization can rescue structural mismatch between Signatures and task characteristics.

This two-level decomposition has practical implications: teams adopting DSPy can expect immediate gains from Signatures on most tasks, and when structural mismatch occurs, automatic optimization provides a reliable recovery mechanism.

% ---------------------------------------------------------------------------
\subsection{Emergent Agent Behavior}
\label{subsec:emergent}
% ---------------------------------------------------------------------------

A noteworthy observation is that the ReAct agent \emph{converges on} structured retrieval protocols.
Despite having access to six core tools with no enforced execution order, the agent consistently converges on a decompose--search--evaluate pattern across all 800+ questions in our evaluation (RQ2, \S\ref{subsec:rq2}).

This emergent behavior suggests that the combination of typed Signatures (providing a recommended protocol), evaluation feedback (providing quality signals), and ReAct reasoning (enabling reflective planning) creates sufficient inductive bias for structured behavior without requiring hard-coded orchestration logic.
The progressive information disclosure pattern (search previews followed by selective full-text retrieval) and domain-adaptive tool selection (\texttt{calculate} on FinanceBench, \texttt{list\_document\_sections} on complex documents) further demonstrate the agent's capacity for sophisticated retrieval strategies that arise purely from the interaction between tools and reasoning.

% ---------------------------------------------------------------------------
\subsection{Limitations and Future Work}
\label{subsec:limitations}
% ---------------------------------------------------------------------------

We acknowledge several limitations:

\begin{enumerate}
    \item \textbf{Retrieval corpus.} We use each dataset's provided context paragraphs rather than a large-scale open-domain corpus (\eg, DPR's Wikipedia dump~\cite{karpukhin2020dense}).
    This ensures controlled evaluation of the refinement mechanism, but limits comparison with methods evaluated on open-domain retrieval.
    The retrieval space saturation observed on FinanceBench (\S\ref{subsec:boundary}) may not generalize to larger enterprise corpora.

    \item \textbf{Model--pipeline interaction.} The Reasoning Model Refusal Asymmetry (\S\ref{subsec:model_interaction}) demonstrates that pipeline effectiveness depends on the base model's reasoning characteristics.
    Our cross-model validation covers two models (Gemini Flash Lite and gpt-5-mini); broader validation across model families (\eg, open-source models such as LLaMA~\cite{touvron2023llama}) and model sizes would strengthen the generalizability claims.

    \item \textbf{Latency.} The 4--5$\times$ latency overhead limits applicability to latency-sensitive scenarios.
    Techniques such as parallel tool execution, speculative decoding, and agent module distillation could mitigate this but are not explored.

    \item \textbf{Structure-aware tools.} The dataset-dependent benefit of structure tools (RQ4) is limited to our evaluation datasets.
    Documents with richer hierarchical structure (\eg, legal contracts, technical manuals, multi-chapter reports) may show stronger benefits, which we leave to future investigation.

    \item \textbf{Evaluation calibration.} The evaluation tool's miscalibration on FinanceBench suggests that domain-specific calibration or learned evaluation thresholds may be necessary for optimal performance across diverse domains.

    \item \textbf{Statistical power.} While our $n = 200$ evaluation with bootstrap significance testing provides rigorous evidence for the 2WikiMultiHopQA result ($p < 0.001$), improvements on HotpotQA and MuSiQue do not reach significance against Loop Refinement.
    Larger-scale evaluation or more powerful statistical tests may be needed to detect smaller effect sizes on these datasets.
\end{enumerate}
