\documentclass[preprint,review,number]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepgfplotslibrary{groupplots}
\usetikzlibrary{positioning, arrows.meta, calc, shapes.geometric, fit, backgrounds, patterns}

\bibliographystyle{elsarticle-num}

% Custom commands
\newcommand{\ours}{\textsc{TARA}}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\cf}{\textit{cf.}}
\newcommand{\etal}{\textit{et al.}}

\journal{Knowledge-Based Systems}

\begin{document}

\begin{frontmatter}

\title{TARA: Complexity-Adaptive Retrieval Refinement through Tool-Augmented ReAct Agents}

\author[1]{Ruo Lee}
\ead{comsa333@gmail.com}
\affiliation[1]{organization={Department of Artificial Intelligence},
               addressline={Seoul School of Integrated Sciences \& Technologies (aSSIST)},
               city={Seoul}, country={South Korea}}

% Second author to be added upon confirmation.
% \author[1]{[Name]\corref{cor1}}
% \cortext[cor1]{Corresponding author}
% \ead{[email]}

\begin{abstract}
Retrieval-Augmented Generation (RAG) has emerged as a practical approach to ground large language model (LLM) outputs in external knowledge.
However, existing self-corrective RAG methods rely on fixed iterative loops with predetermined refinement strategies, limiting their ability to adapt to varying question complexity.
We propose \ours{}, a framework that replaces fixed-loop refinement with a ReAct-based agent equipped with six specialized tools---passage search, query decomposition, quality evaluation, passage inspection, document structure browsing, and terminology mapping.
The agent autonomously reasons about retrieval quality and selects appropriate tools in a Thought--Action--Observation loop, enabling adaptive refinement depth proportional to question complexity.
The entire pipeline is implemented as a DSPy declarative program, enabling automatic prompt optimization through BootstrapFewShot and MIPROv2.
Experiments on four datasets ($n = 200$; HotpotQA, 2WikiMultiHopQA, MuSiQue, and FinanceBench) with bootstrap significance testing demonstrated that \ours{} achieved statistically significant F1 improvement of +0.089 on 2WikiMultiHopQA ($p < 0.001$), with consistent positive trends on MuSiQue (+0.039).
Cross-model validation with gpt-5-mini revealed a model--pipeline interaction effect where reasoning-oriented models exhibit refusal asymmetry in agentic pipelines. This finding provides evidence for model-aware pipeline selection.
DSPy's typed signatures alone improved F1 by 0.075--0.190 on three of four datasets over manual prompt engineering, with automatic optimization yielding further gains.
Ablation studies confirmed that the evaluation tool functions as a quality gate mechanism, structure-aware tools provide dataset-dependent benefits, and the agent converges on structured retrieval protocols.
\end{abstract}

\begin{highlights}
\item TARA: ReAct agent with six tools for autonomous retrieval refinement
\item Statistically significant F1 +0.089 on 2WikiMultiHopQA ($p < 0.001$, $n = 200$)
\item Cross-model validation reveals model--pipeline interaction effect (refusal asymmetry)
\item DSPy typed signatures boost F1 by 0.075--0.190 over manual prompt engineering
\item Comprehensive ablation with bootstrap significance testing across four datasets
\end{highlights}

\begin{keyword}
retrieval-augmented generation \sep
agentic refinement \sep
tool-augmented language model \sep
DSPy \sep
multi-hop question answering \sep
self-corrective retrieval
\end{keyword}

\end{frontmatter}

%% ====================================================================
\section{Introduction}
\label{sec:introduction}
%% ====================================================================

\input{sections/introduction}

%% ====================================================================
\section{Related Work}
\label{sec:related}
%% ====================================================================

\input{sections/related_work}

%% ====================================================================
\section{Method}
\label{sec:method}
%% ====================================================================

\input{sections/method}

%% ====================================================================
\section{Experimental Setup}
\label{sec:setup}
%% ====================================================================

\input{sections/setup}

%% ====================================================================
\section{Results and Analysis}
\label{sec:results}
%% ====================================================================

\input{sections/results}

%% ====================================================================
\section{Ablation Studies}
\label{sec:ablation}
%% ====================================================================

\input{sections/ablation}

%% ====================================================================
\section{Discussion}
\label{sec:discussion}
%% ====================================================================

\input{sections/discussion}

%% ====================================================================
\section{Conclusion}
\label{sec:conclusion}
%% ====================================================================

\input{sections/conclusion}

%% ====================================================================
%% References
%% ====================================================================

%% ====================================================================
%% Required Elsevier/KBS Elements
%% ====================================================================

\section*{CRediT authorship contribution statement}

\textbf{Ruo Lee}: Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data curation, Writing -- original draft, Writing -- review \& editing, Visualization.
% Second author CRediT to be added upon confirmation.
% \textbf{[Name]}: Supervision, Writing -- review \& editing.

\section*{Declaration of competing interest}

The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

\section*{Data availability}

All multi-hop QA datasets (HotpotQA, 2WikiMultiHopQA, MuSiQue) are publicly available. FinanceBench is available under CC-BY-NC-4.0.
Code and experiment configurations are available at \url{https://github.com/comsa33/self-corrective-rag}.

\section*{Declaration of generative AI and AI-assisted technologies in the writing process}

During the preparation of this work, the author used Claude (Anthropic) for code development assistance and manuscript drafting support.
After using this tool, the author reviewed and edited the content as needed and takes full responsibility for the content of the publication.

\bibliography{references}

\end{document}
